Tidal field anisotropy as a tracer of cosmic voids

### 2015-02-13 cosmic_voids.tex
revisado velocity profile

The left column in Figure \ref{fig:RhoVel} shows the results of
stacked density profiles for different void sizes. 
We normalize the radial coordinate with the effective radius to check
for possible universal features among voids. 
We calculate the profile out to a radius $8\ \reff$  to capture the
the point where the overdensity reaches the mean value.

@@

Another important result is the steepness of the profiles at inner
regions. For subcompensated voids, larger voids are more steep, reaching
the mean density value at lower radius. Smaller voids exhibit moderate
slopes, reaching the mean density at much larger radius. This indicates 
smaller subcompensated voids are embedded into low density structures like 
larger voids and still forming regions like walls. For subcompensated large
voids, outer radial layers are so vast that all sort of structures are 
stacked, thus reaching the mean density at lower radius. This result 
remains also for overcompensated voids, where larger voids reach first 
both, the compensation ridge and then the mean density value.

@@

All the previous results hold for both finding schemes, thereby pointing 
out to an universal radial profile of voids (subcompensated and 
overcompensated), and not only for the internal structure \citep{Colberg05, 
Ricciardelli2013}, but also for outer regions \citep{Lavaux12, Hamaus14}.

@@

Additionally, in middle panels of Fig. \ref{fig:RhoVel} we calculate 
radial projected velocity profiles, where positive values implies outflow 
of matter, while negative ones indicates infall flows, all from the void 
centre.

A general feature of subcompensated voids is outward velocity profiles, 
indicating that matter all along these voids and their outsides is being 
pulled out. On the other hand, overcompensated voids exhibit initially
outward profiles, as expected from a low density region. However, 
approximately at the radius of the compensation ridge, the velocity becomes 
negative, thus indicating an infall flow of matter further than the 
compensation ridge. This shows that the high density structures associated 
to a compensation ridge indeed dominate the matter flow from inside the void 
as well as falling flows from outsides.

All the profiles behave linearly near to the void centres, where larger 
voids display more steep slopes. This indicates larger voids are being
pulled out more strongly by nearby structures. On the other hand, at 
large radius, all the profiles decrease to the zero background velocity,
where larger voids reach this value first as their outer radial layers 
average a large portion of volume.

Like the density, these results also point out to an universal radial 
velocity profiles of voids \citep{Hamaus14}.

>>>>

Figure \ref{fig:density_profile} shows the results of stacked density
profiles for different void sizes.  
We normalize the radial coordinate with the effective radius to check
for possible universal features among voids. 
We calculate the profile out to a radius $8\ \reff$  to capture the
the point where the overdensity reaches the mean value.

@@

A second feature about these profiles is their steepnes at inner
regions.  
In subcompensated voids, larger voids are steeper.
Smaller voids exhibit moderate slopes, reaching the mean density at
larger radii than larger voids.
This suggests that smaller subcompensated voids are embedded into low
density structures like voids or walls, while arge subcompensated
voids are surrounded  by dense structures, reaching the mean density
at lower effective radii than smaller voids.
In overcompensated voids larger voids reach first  both the
compensation ridge and then the mean density value.

@@

All the previous results hold for both finding schemes.
This suggests an universal behaviour for the radial density profile in
two families of subcompensated and overcompensanted voids. 
This goes in the same direction of recent results about the internal
\citep{Colberg05,  Ricciardelli2013} and external structure of voids
\citep{Lavaux12, Hamaus14}. 
Our results extend the findings of \cite{Hamaus14} into the range of
voids with size $r_{\rm eff}<10$\hMpc.

@@

In Figure \ref{fig:velocity_profile} we present the radial velocity
profiles. 
Positive values correspond to outflows with respect to the center.

We find that subcompensated voids have outflowing velocity profiles
all the way up to the effective radius where the average radial
density reaches the average value.
For voids with sizes $r_{\rm eff}<8$\hMpc the outflow is always
positive, consistent with the fact that their density profiles do not
reach the level $\delta=0$ in the range of explored radii.
This behaviour indicates that matter is being pulled out of the void
into external higher density features.

On the other hand, overcompensated voids initially exhibit and outward
profiles, (as expected from a low density region) and approximately at
the radius of the compensation ridge, the velocity reaches a peak,
decreases and becomes negative, showing the infalling flow of matter
further than the compensation ridge. 
This shows that the high density structures associated to the
compensation ridge dominate the matter flow both from inside and
outside the void.

As in the density these results also consistent with a Universial
velocity profile for voids \citep{Hamaus14}.
